\section{Conclusion and Future Work}\label{sec:conclusion-and-future-work}

The MorteSense DIY security system represents a significant step forward in providing
accessible and reliable security solutions for both residential and commercial properties. %
By integrating microwave motion sensors and SMS notifications, the system offers an
affordable and user-friendly approach to monitoring and securing properties with ease of
repair and maintenance in mind. %

The project ensured the creation of an intuitive user interface, compatibility with a variety
of devices, and the establishment of a robust and secure system that is easy to install and operate. %
The system's focus on real-time alerts through SMS notifications enables prompt responses to
potential security breaches, ultimately contributing to enhanced safety and security for
homeowners and businesses alike. %

The project's approach to leveraging contemporary microcontrollers and Wi-Fi connectivity, along
with its modular design principles, underscores the system's adaptability and potential for
future expansion. %
Furthermore, the integration of a user-friendly web interface and the incorporation of Twilio API for SMS notifications contribute to the overall accessibility
and sustainability of the system. %
By considering factors such as user behavior, power outages,and software compatibility, the system was designed to mitigate these risks and ensure a
robust security solution for end-users. %

The comprehensive documentation, including the PCB diagram and Class Diagram, highlights the
meticulous planning and execution involved in the hardware and software integration. %
This careful attention to detail ensures a seamless data flow and an effective user experience,
further emphasizing the system's reliability and user-friendliness. %

Additionally, the incorporation of advanced technologies such as blockchain and machine
learning, while beyond the current scope, presents promising avenues for further
research and development in the field of smart home security systems. %

In summary, the MorteSense DIY security system's innovative use of technology, combined with
its emphasis on accessibility and user-friendliness, makes it a valuable and practical
solution for those seeking openly-documented security measures for their homes and businesses. %

